Kronos \& Krios: Evidence for accretion of a massive, rocky planetary system in a comoving pair of solar-type stars

### 2017-09-15 paper/ms.tex
tweak caption

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.95\linewidth]{deltaxh_tcrank.pdf}
  \caption{
    Comparing the observed abundance difference (blue circles) to the expected
    change in solar surface abundance after adding \maccreted\ of material
    with bulk Earth composition (\citealt{2003TrGeo...2..547M}; black open and
    filled circles).
    The assumed mass fraction in the convective zone is $0.02$.
    All astronomical metals are ordered by their \Tcondens\ for solar
    composition gas on the $x$-axis.
    For the predictions, we highlight elements measured for \bizarreone-\sunanalog\ pair
    in filled circles, while those without a measurement are left open.
    The close match with the observed abundance difference in \bizarreone-\sunanalog\ pair
    suggests that the abundance difference may be due to accretion of
    $15$~\mearth\ of rocky planetary material.
    The element \elem{Li} is off the plot and indicated in the inset.
  }
  \label{fig:toycalc}
\end{figure}

>>>>

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.95\linewidth]{deltaxh_tcrank.pdf}
  \caption{
    Comparing the observed abundance difference ($\bizarreone-\sunanalog$; blue
    circles) to the expected change in solar surface abundance after adding
    \maccreted\ of material with bulk Earth composition
    (\citealt{2003TrGeo...2..547M}; black open and filled circles).
    The assumed mass fraction in the convective zone is $0.02$.
    All astronomical metals are ordered by their \Tcondens\ for solar
    composition gas on the $x$-axis.
    For the predictions, we highlight elements measured for \bizarreone-\sunanalog\ pair
    in filled circles, while those without a measurement are left open.
    The close match with the observed abundance difference in \bizarreone-\sunanalog\ pair
    suggests that the abundance difference may be due to accretion of
    $15$~\mearth\ of rocky planetary material.
    The element \elem{Li} is off the plot and indicated in the inset.
  }
  \label{fig:toycalc}
\end{figure}
